---
title: 'Lab 7: multiple linear regression intro'
author: "Mari Herbst"
date: "11/9/2021"
output: html_document
---

```{r setup, include = TRUE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

library(tidyverse)
library(palmerpenguins)
library(GGally)
library(broom)
library(kableExtra)
library(modelsummary)
library(stargazer)
```

## Explore penguins

Use 'GGally::ggpairs()' to create a pairs plot.

```{r}
ggpairs(penguins)
```

That's kind of overkill. Let's simplify the variables that we include in our ggpairs plot:

- species
- bill_lenth_mm through body_mass_g

```{r}
penguins %>%
  select(species, bill_length_mm:body_mass_g) %>%
  ggpairs(aes(color = species))
```

## Multiple linear regression

We are going to try to understand (a bit better) relationships between multiple predictor variables and an outcome which is penguin body mass.

The different predictor variables we're going to try are:

- species
- flipper length
- sex
- bill depth

### Model 1

Model body mass based on only flipper length and bill depth (bad idea. there are important variables missing).

```{r}
model_1 <- lm(body_mass_g ~ flipper_length_mm + bill_depth_mm, data = penguins)

# Call model by name to return only coefficients:
model_1

# More information on the coefficients and model:
summary(model_1)
```

Coefficient interpretation: we would expect, on average, a 51.54g increase in body mass for every 1mm increase in flipper length, if all other variables are constant.

R-squared interpretation: 76% of variance in the penguin body mass (dependent variable) is explained by flipper length and bill depth.

Actually -- we think that a model for penguin body mass should contain the variables species, flipper length, and penguin sex

```{r}
model_2 <- lm(body_mass_g ~ species + flipper_length_mm + sex, data = penguins)

# call the model to see coefficients
model_2

# more info about the model
summary(model_2)
```

reference species: Adelie, reference sex: female

coefficient interpretation:
- flipper length: if all else stays constant, we would expect on average a 20.02g increase in body mass for every 1mm increase in flipper length
- Gentoo: if all else stays constant, we would expect on average a Gentoo penguin would have an 836.26g higher body mass than an Adelie penguin with the same other characteristics
- sexmale: if all else stays constant, we would expect a male penguin to be on average 530.38g larger than a female penguin with the same other characteristics

## Visualize this model

```{r}
ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g)) +
  geom_point(aes(color = species)) +
  facet_wrap(~ sex)
```

## A couple ways to get an report multiple linear regression model outcomes

Use broom::tidy() to get model coefficient info in a tidy data frame.

```{r}
penguin_model2_coeff <- tidy(model_2)

penguin_model2_coeff
```

Inline code that spits out the coefficient for Gentoo:
`r penguin_model2_coeff$estimate[3]`

## Look at model diagnostics

Use the plot() function:

```{r}
plot(model_2)
```

residuals vs. fitted: no trend to higher or lower across the data
normal q-q: shows normality of data dist
residuals vs. leverage: shows if there are outliers (if there is a point past the Cook's distance line)

## Report the model outputs in a summary table

Use modelsummary():

```{r}
modelsummary(model_2)
```

Use stargaser():

```{r, results = "asis"}
stargazer(model_2, model_1, type = "html")
```

